
\begin{thebibliography}{99}
\begin{sloppypar}

% Javier REFS
\bibitem{alexa-twitter}Alexa - Twitter.com site info. [en línea]\textless \url{http://www.alexa.com/siteinfo/twitter.com}\textgreater[consulta: 30 Octubre 2012] 


%Capitulo 1
\bibitem{WileyWSN} SOHRABY, Kazem. MINOLI, Daniel. ZNATI, Taiebi. Wireless sensor networks: technology, protocols, and applications. Editorial John Wiley \& Sons, Inc. 2007.

\bibitem{WSNSurvey} AL-KARAKI, Jamal N. KAMAL, Ahmed E. Routing Techniques in Wireless Sensor Networks: A Survey. The Hashemite University, Iowa State University. 2004.

\bibitem{ProyectoForestal} Redes inalámbricas de sensores para la detección de incendios forestales y monitoreo de variables de estado de combustibles para el recurso forestal de la Región de Valparaíso. [en línea]\textless \url{http://www.gisincendiosforestales.cl}\textgreater[consulta: 15 junio 2009] 

\bibitem{Wiseconn} Wiseconn - Wireless Sensors. [en línea]\textless \url{http://www.wiseconn.cl/}\textgreater[consulta: 15 junio 2009] 

\bibitem{LeachOriginal} HEINZELMAN, Wendi. CHANDRAKASAN, Anantha. BALAKRISHNAN, Hari. Energy-Efficient Communication Protocol for Wireless  Microsensor Network. Massachusetts Institute of Technology, Cambridge. 2000. [en línea]\textless \url{http://ieeexplore.ieee.org/xpl/freeabs_all.jsp?arnumber=926982}\textgreater[consulta: 20 junio 2008] 

\bibitem{PegasysOriginal} LINDSEY, Stephanie. RAGHAVENDRA, Cauligi. PEGASIS: Power-Efficient Gathering in Sensor Information Systems. Computer Systems Research Department. The Aerospace Corporation. 2003. [en línea]\textless \url{http://ieeexplore.ieee.org/xpl/freeabs_all.jsp?arnumber=1035242}\textgreater[consulta: 20 junio 2008] 

\bibitem{HeedOriginal} YOUNIS, Ossama. FAHMY, Sonia. HEED: A Hybrid, Energy-Efficient, Distributed Clustering Approach for Ad-hoc Sensor Networks. Department of Computer Sciences, Purdue University. 2004. [en línea]\textless \url{http://ieeexplore.ieee.org/xpl/freeabs_all.jsp?arnumber=1035242}\textgreater[consulta:  2 julio 2009] 

\bibitem{TeenOriginal} MANJESHWAR, Arati. AGRAWAL, Dharma. TEEN: A Routing Protocol for Enhanced Efficiency in Wireless Sensor Networks. Center of Distributed and Mobile Computing, ECECS Department, University of Cincinnati, Cincinnati. 2002. [en línea]\textless \url{http://ieeexplore.ieee.org/xpl/freeabs_all.jsp?arnumber=925197}\textgreater[consulta: 20 junio 2008] 

\bibitem{TEP118} LEVIS, Philip. TOLLE, Gilman. TEP 118: Dissemination of Small Values. TinyOS Net2 Working Group. 2007. 
[en línea]\textless \url{http://www.tinyos.net/tinyos-2.x/doc/html/tep118.html}\textgreater[consulta: 21 junio 2008] 

\bibitem{TEP123} FONSECA, Rodrigo. GNAWALI, Omprakash. JAMIESON, Kyle. KIM, Sukun. LEVIS, Philip. WOO, Alec. TEP 123: The Collection Tree Protocol. TinyOS Network Working Group. 2007. [en línea]\textless\url{http://www.tinyos.net/tinyos-2.x/doc/html/tep123.html}\textgreater[consulta: 21 junio 2008] 

\bibitem{IntelMote2Web} ''Intel Mote 2 - Platformx Wiki". [en línea]\textless\url{http://embedded.seattle.intel-research.net/wiki/index.php?title=Intel_Mote_2}\textgreater[consulta: 3 marzo 2010] 

\bibitem{IrisDatasheet} '' Iris Datasheet ''. Crossbow Technology. [en línea]\textless\url{http://www.xbow.com/Products/Product_pdf_files/Wireless_pdf/IRIS_Datasheet.pdf}\textgreater[consulta: 3 marzo 2010] 

\bibitem{Mica2Datasheet} ''Mica2 Datasheet ''. Crossbow Technology.
[en línea]\textless\url{http://www.xbow.com/Products/Product_pdf_files/Wireless_pdf/MICA2_Datasheet.pdf}\textgreater[consulta: 3 marzo 2010] 

\bibitem{MicazDatasheet} ''Micaz Datasheet ''. Crossbow Technology.
[en línea]\textless\url{http://www.xbow.com/Products/Product_pdf_files/Wireless_pdf/MICAz_Datasheet.pdf}\textgreater[consulta: 3 marzo 2010] 

\bibitem{ShimmerWiki} ''Shimmer - TinyOS Documentation Wiki''.
[en línea]\textless\url{http://docs.tinyos.net/index.php/SHIMMER}\textgreater[consulta: 3 marzo 2008] 

\bibitem{TelosBDatasheet} ''TelosB Datasheet ''. Crossbow Technology.
[en línea]\textless\url{http://www.xbow.com/Products/Product_pdf_files/Wireless_pdf/TelosB_Datasheet.pdf}\textgreater[consulta: 3 marzo 2020] 

\bibitem{TinyNodeWeb} ''TinyNode''.
[en línea]\textless\url{http://www.tinynode.com}\textgreater[consulta: 3 marzo 2010] 

\bibitem{ATAVRRZ201} ''Atmel Products - MCU Wireless - ATAVRRZ201''. Atmel Corporation.
[en línea]\textless\url{http://www.atmel.com/dyn/products/tools_card_v2.asp?tool_id=4186}\textgreater[consulta: 3 marzo 2010] 

%Capítulo 2
\bibitem{TelosBConsumo} POLASTRE, Joseph. SZEWCZYK, Robert. CULLER, David. Telos: Enabling Ultra-Low Power Wireless Research. Computer Science Department, University of California, Berkeley. 2005. 
[en línea]\textless\url{http://ieeexplore.ieee.org/xpl/freeabs_all.jsp?arnumber=1440950}\textgreater[consulta: 30 Agosto 2009] 

\bibitem{EmbeddedArchitecture} LEVIS, Philip. Embedded Sensor Architecture. Stanford University. Stanford. 2005.
[en línea]\textless\url{http://csl.stanford.edu/ ˜pal/talks/ee282-f05-sensors.pdf}\textgreater[consulta: 31 Agosto 2009]

\bibitem{LeachOptimo} YANG, Haiming. SIKDAR, Biplab. Optimal Cluster Head Selection in the LEACH Architecture. Department of ECSE, Rensselaer Polytechnic Institute. 2007.
[en línea]\textless \url{http://ieeexplore.ieee.org/xpl/freeabs_all.jsp?arnumber=4197919}\textgreater[consulta: 21 junio 2008] 

\bibitem{mumhr} HAMMOUDEH, Mohammad. KURZ, Alexander. GAURA, Elena. MuMHr: Multi-path, Multi-hop Hierarchical Routing. Cogent Computing Applied Research Centre, Coventry University. 2007.
[en línea]\textless \url{http://ieeexplore.ieee.org/xpl/freeabs_all.jsp?arnumber=4394911}\textgreater[consulta: 14 Octubre 2008] 

\bibitem{mleach} MHATRE, V. ROSENBERG, C. Homogeneous vs Heterogeneus Clustered Sensor Networks: A Comparative Study. 2004.
[en línea]\textless \url{http://ieeexplore.ieee.org/xpl/freeabs_all.jsp?arnumber=1313223}\textgreater[consulta: 14 Octubre 2008]

\bibitem{hpegasis} LINDSEY, Stephanie. RAGHAVENDRA, Cauligi. Data Gathering in Sensor Networks using the Energy*Delay Metric. Computer Systems Research Department, The Aerospace Corporation. 2002.
[en línea]\textless \url{http://ieeexplore.ieee.org/xpl/freeabs_all.jsp?arnumber=925196}\textgreater[consulta: 14 Octubre 2008] 

\bibitem{What2ndGenHolds} LEVIS, Philip. What the Second Generation Holds. Presentación para la Stanford University. 2007.
[en línea]\textless \url{http://www.youtube.com/watch?v=j6hRsue5b30}\textgreater[consulta: 8 Octubre 2008] 

\bibitem{TricklePaper} LEVIS, Philip. PATEL, Neil. CULLER, David. SHENKER, Scott. Trickle: A Self-Regulating Algorithm for Code Propagation and Maintenance in Wireless Sensor Networks. 2004. University of California, Berkeley.

[en línea]\textless \url{http://csl.stanford.edu/~pal/pubs/trickle-nsdi04.pdf}\textgreater[consulta: 16 Junio 2009] 

\bibitem{PaperComparacion} SEON, Choong. THUA, Trong. Delay Efficient Multi-Hop Routing Secheme for 
Wireless Sensor Networks. 2006.
[en línea]\textless \url{http://portal.acm.org/citation.cfm?id=1185006}\textgreater[consulta: 26 Marzo 2009] 

%Capítulo 4
\bibitem{TinyOSProgramming} LEVIS, Philip. GAY, David. TinyOS Programming. Editorial Cambridge University Press. 2009.

\bibitem{FtspBug}PacketTimeStamp CC2420 bug.
[en línea]\textless \url{http://docs.tinyos.net/index.php/PacketTimeStamp_CC2420_bug}\textgreater[consulta: 31 Agosto 2009] 

\bibitem{IEEE802154} IEEE 802.15 WPAN TASK GROUP 4. IEEE Standard for information technology-Telecommunications and information exchange between systems-Local and metropolitan area networks-Specific requirements, Part 15.4: Wireless Medium Access Control (MAC) and Physical Layer (PHY) Specifications for Low-Rate Wireless Personal Area Networks (WPANs). IEEE Computer Society. 2006.

\bibitem{RSSIUnder} SRINIVASAN, Kannan. LEVIS, Philip. RSSI is Under Appreciated. Departmen of Electrical Engineering, Department of Computer Science, Standford University. 2006.
[en línea]\textless \url{http://csl.stanford.edu/~pal/pubs/emnets06.pdf}\textgreater[consulta: 21 noviembre 2009] 

%Capítulo 5
\bibitem{Net2WG} Net2WG - TinyOS 2.x Working Group.
[en línea]\textless \url{http://tinyos.stanford.edu:8000/Net2WG}\textgreater[consulta: 2 noviembre 2009] 

\end{sloppypar}
\end{thebibliography}
